### 2018-09-19 articleSFDS.tex
ajout dans le tableau des nouveaux M2' et M4'

\begin{table}[htbp!]
\centering
\caption{Comparison of the RMSEs and coverage rates in prediction of 100 test-sets on three randomly selected days.}
\label{tab:comparison}
\begin{tabular}{c|c|c|c|c}

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$\\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 32 & 87 & 23 \\
\hline
RMSE of the instantaneous power ($W$) & 12.69 & 21.61 & 5.91 & 18.7 \\
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp!]
\centering
\caption{Comparison of the RMSEs and coverage rates in prediction of 100 test-sets on three randomly selected days where $\mathcal{M}_2'$ and $\mathcal{M}_4'$ are the models based on the Gaussian process established after the sequential design}
\label{tab:comparison}
\begin{tabular}{c|c|c|c|c|c|c}

& $\mathcal{M}_1$ & $\mathcal{M}_2$ & $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_2'$&  $\mathcal{M}_4'$ \\
\hline
\hline
coverage rate at 90\% (in \%) & 91 & 32 & 87 & 23 & 54 & 0 \\
\hline
RMSE of the instantaneous power ($W$) & 12.69 & 21.61 & 5.91 & 18.7 & 7.95 & 0 \\
\end{tabular}
\end{table}
